Paper figures

### 2020-11-26 notebooks/paper_plots_0909.Rmd
added go colored effector sensor plots to paper plots

```{r}
library(reticulate)
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
```

@@

pcc_degree_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
    #geom_density()+
    geom_line(data=     pcc_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data=     pcc_df%>%filter(group=='random'),aes(x=deg,y=..scaled.., color=group, fill=random_id),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    theme_bw()+
    xlab('Degree')+
    ylab('Density')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())#+theme_fontsize
pcc_eff_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
#    geom_density()+
    geom_line(data= pcc_df%>%filter(group=='real'),
               aes(x=eff_norm ,y=..scaled.., color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= pcc_df%>%filter(group=='random'),
               aes(x=eff_norm ,y=..scaled..,fill=random_id, color=group),
               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    ylab('Density')+
    xlab('Effectiveness')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())#+theme_fontsize+
#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
pcc_sensitivity_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data), scales='free_y')+
#    geom_density()+
    geom_line(data= pcc_df%>%filter(group=='real'),
               aes(x=sens_norm,y=..scaled.. , color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= pcc_df%>%filter(group=='random'),
               aes(x=sens_norm,y=..scaled..,fill=random_id,color=group),
               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    xlab('Sensitivity')+
    ylab('Density')+
    coord_trans(x = "log10")+
    scale_color_discrete(labels=c('Rewired networks','Real network'))+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
# scale_y_continuous(
#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
#theme_fontsize+
#annotate("text", x = 0.001, y = 0.9, label=sprintf("p = %#.2f", sens_p), fontface='italic', size=6)
title <- cowplot::ggdraw() + cowplot::draw_label("Costanzo 2016 network", fontface='bold')
pcc_dens_comb = cowplot::plot_grid(pcc_degree_dens+theme(legend.position='none'), 
                                pcc_eff_dens+theme(legend.position='none'), 
                                pcc_sensitivity_dens+theme(legend.position='none'), labels=c('A','B','C'),ncol=3)
pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))

yuri_degree_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
    #geom_density()+
    geom_line(data=     yuri_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data=     yuri_df%>%filter(group=='random'),aes(x=deg,y=..scaled.., color=group, fill=random_id),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    theme_bw()+
    xlab('Degree')+
    ylab('Density')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())#+theme_fontsize
yuri_eff_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
#    geom_density()+
    geom_line(data= yuri_df%>%filter(group=='real'),
               aes(x=eff_norm ,y=..scaled.., color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= yuri_df%>%filter(group=='random'),
               aes(x=eff_norm ,y=..scaled..,fill=random_id, color=group),
               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    ylab('Density')+
    xlab('Effectiveness')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())#+theme_fontsize+
#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
yuri_sensitivity_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data), scales='free_y')+
#    geom_density()+
    geom_line(data= yuri_df%>%filter(group=='real'),
               aes(x=sens_norm,y=..scaled.. , color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= yuri_df%>%filter(group=='random'),
               aes(x=sens_norm,y=..scaled..,fill=random_id,color=group),
               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    xlab('Sensitivity')+
    ylab('Density')+
    coord_trans(x = "log10")+
    scale_color_discrete(labels=c('Rewired networks','Real network'))+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
# scale_y_continuous(
#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
title <- cowplot::ggdraw() + cowplot::draw_label("Yeast PPI network", fontface='bold')
yuri_dens_comb = cowplot::plot_grid(yuri_degree_dens+theme(legend.position='none'), 
                                yuri_eff_dens+theme(legend.position='none'), 
                                yuri_sensitivity_dens+theme(legend.position='none'), labels=c('D','E','F'),ncol=3)
yuri_dens_comb_title = cowplot::plot_grid(title, yuri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))

huri_degree_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
    #geom_density()+
    geom_line(data=     huri_df%>%filter(group=='real'),aes(x=deg,y=..scaled..,color=group),stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data=     huri_df%>%filter(group=='random'),aes(x=deg,y=..scaled.., color=group, fill=random_id),stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    theme_bw()+
    xlab('Degree')+
    ylab('Density')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())#+theme_fontsize
huri_eff_dens <- 
    ggplot()+
    #facet_grid(rows=vars(data))+
#    geom_density()+
    geom_line(data= huri_df%>%filter(group=='real'),
               aes(x=eff_norm ,y=..scaled.., color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= huri_df%>%filter(group=='random'),
               aes(x=eff_norm ,y=..scaled..,fill=random_id, color=group),
               stat = 'density',linetype = "dashed" )+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    ylab('Density')+
    xlab('Effectiveness')+
    coord_trans(x = "log10")+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 ) +
theme(panel.grid.minor = element_blank())#+theme_fontsize+
#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
huri_sensitivity_dens <- 
    ggplot()+
#$    facet_grid(rows=vars(data), scales='free_y')+
#    geom_density()+
    geom_line(data= huri_df%>%filter(group=='real'),
               aes(x=sens_norm,y=..scaled.. , color=group),
               stat = 'density')+#, binwidth = 0.1) + 
    geom_line(data= huri_df%>%filter(group=='random'),
               aes(x=sens_norm,y=..scaled..,fill=random_id,color=group),
               stat = 'density',linetype = "dashed")+#, binwidth = 0.1) + 
    #geom_histogram(binwidth=0.0001)+
    theme_bw()+
    xlab('Sensitivity')+
    ylab('Density')+
    coord_trans(x = "log10")+
    scale_color_discrete(labels=c('Rewired networks','Real network'))+
scale_x_continuous(
   breaks = scales::trans_breaks("log10", function(x) 10^x),
   labels = scales::trans_format("log10", scales::math_format(10^.x))
 )+ 
# scale_y_continuous(
#   breaks = scales::trans_breaks("log1p", function(x) 10^(1+x)),
#   labels = scales::trans_format("log10", scales::math_format(10^.x))
# ) +
theme(panel.grid.minor = element_blank(), legend.position='bottom', legend.title=element_blank())
title <- cowplot::ggdraw() + cowplot::draw_label("HuRI network", fontface='bold')
huri_dens_comb = cowplot::plot_grid(huri_degree_dens+theme(legend.position='none'), 
                                huri_eff_dens+theme(legend.position='none'), 
                                huri_sensitivity_dens+theme(legend.position='none'), labels=c('G','H','I'),ncol=3)
huri_dens_comb_title = cowplot::plot_grid(title, huri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
dens_plots = cowplot::plot_grid(pcc_dens_comb_title,
                                yuri_dens_comb_title,
                                huri_dens_comb_title,nrow=3)
cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
ggsave('reports/figures/paper_figures_0916/fig1.png')

@@

```{r}
convert_networkx_to_igraph <- 			# 
    function
(
 	nx_object,
    df
)
{
    nx =  reticulate::import("networkx")
    ig = igraph::graph.adjacency(nx$adjacency_matrix(nx_object), mode = 'undirected')
    #ig = igraph::set_vertex_attr(ig , name =  'orf_name', value  = (df$orf_name))
    ig = igraph::set_vertex_attr(ig , name =  'name', value  = (df$orf_name))
    #igraph::set_vertex_attr(ig, "pos", nx_object$nodes('pos'))
    ig
}
```

>>>>

```{r}
library(reticulate)
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
source('src/R/plot_density_prs.R')
```

@@

pcc_degree_dens <- 
    plot_density_prs(pcc_df, deg, xlab='Degree')
pcc_eff_dens <- 
    plot_density_prs(pcc_df, eff_norm, xlab='Effectiveness')
#annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
pcc_sensitivity_dens <- 
    plot_density_prs(pcc_df, sens_norm, xlab='Sensitivity')
title <- cowplot::ggdraw() + cowplot::draw_label("Costanzo 2016 network", fontface='bold')
pcc_dens_comb = cowplot::plot_grid(pcc_degree_dens+theme(legend.position='none'), 
                                pcc_eff_dens+theme(legend.position='none'), 
                                pcc_sensitivity_dens+theme(legend.position='none'), labels=c('A','B','C'),ncol=3)
pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
yuri_degree_dens <- 
    plot_density_prs(yuri_df, deg, xlab='Degree')
yuri_eff_dens <- 
    plot_density_prs(yuri_df, eff_norm, xlab='Effectiveness')
yuri_sensitivity_dens <- 
    plot_density_prs(yuri_df, sens_norm, xlab='Sensitivity')
title <- cowplot::ggdraw() + cowplot::draw_label("Yeast PPI network", fontface='bold')
yuri_dens_comb = cowplot::plot_grid(yuri_degree_dens+theme(legend.position='none'), 
                                yuri_eff_dens+theme(legend.position='none'), 
                                yuri_sensitivity_dens+theme(legend.position='none'), labels=c('D','E','F'),ncol=3)
yuri_dens_comb_title = cowplot::plot_grid(title, yuri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
huri_degree_dens <- 
    plot_density_prs(huri_df, deg, xlab='Degree')
huri_eff_dens <- 
    plot_density_prs(huri_df, eff_norm, xlab='Effectiveness')
huri_sensitivity_dens <- 
    plot_density_prs(huri_df, sens_norm, xlab='Sensitivity')
title <- cowplot::ggdraw() + cowplot::draw_label("HuRI network", fontface='bold')
huri_dens_comb = cowplot::plot_grid(huri_degree_dens+theme(legend.position='none'), 
                                huri_eff_dens+theme(legend.position='none'), 
                                huri_sensitivity_dens+theme(legend.position='none'), labels=c('G','H','I'),ncol=3)
huri_dens_comb_title = cowplot::plot_grid(title, huri_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
dens_plots = cowplot::plot_grid(pcc_dens_comb_title,
                                yuri_dens_comb_title,
                                huri_dens_comb_title,nrow=3)
cowplot::plot_grid(dens_plots, dens_lgn,nrow=2,rel_heights=c(.9,.1))
ggsave('reports/figures/paper_figures_0916/fig1.png')

@@

```{r}
convert_networkx_to_igraph <- 			# 
    function
(
 	nx_object,
    df
)
{
    nx =  reticulate::import("networkx")
    ig = igraph::graph.adjacency(nx$adjacency_matrix(nx_object), mode = 'undirected')
    #ig = igraph::set_vertex_attr(ig , name =  'orf_name', value  = (df$orf_name))
    ig = igraph::set_vertex_attr(ig , name =  'name', value  = (df$orf_name))
    #igraph::set_vertex_attr(ig, "pos", nx_object$nodes('pos'))
    ig
}
```
```{r}
library(RColorBrewer)
col = brewer.pal(n=9, name='Set1')
sensor_colors =col[1:6] #brewer.pal(n = 6, name = "Set1")
effector_colors = col[7:9]#brewer.pal(n=3, name= "Set1_r")
```

```{python}
sensor_colors = r.sensor_colors
effector_colors = r.effector_colors
sensors_pcc = e_pcc.df.loc[e_pcc.df.sens>np.quantile(e_pcc.df.sens,0.99)]
#sensor_sub_pcc = get_subnetwork(e_pcc.graph_gc, sensors_pcc.orf_name.values)
#is_sensor = dict(zip(sensor_sub_pcc.nodes, [True if i in sensors_pcc.orf_name.values else False  for i in sensor_sub_pcc.nodes]))
#nx.set_node_attributes(sensor_sub_pcc, is_sensor, 'is_sensor')
sensor_go_terms_separate = [
    'iron ion\ntransport',
    'phenylalanine\ntransport',
    None, 
    None,
    None,
    None,
    'tricarboxylic\nacid cycle', 
    'hexose metabolic\nprocess',
    'protein folding',
    'mitochondria-nucleus\nsignaling pathway/TCA',
    None,
    None,
    None,
    None,
    None,
    None,
    None,
]
sensor_connected_components = sorted([sorted(list(i)) for i in nx.connected_components(nx.induced_subgraph(e_pcc.graph_gc, sensors_pcc.orf_name))], key=lambda x: x[0])
sensor_go_terms= {}
for i in range(len(sensor_go_terms_separate)):
    for j in sensor_connected_components[i]:
        sensor_go_terms[j] = sensor_go_terms_separate[i]
sensors_pcc = sensors_pcc.merge(pd.DataFrame.from_dict(sensor_go_terms,orient='index',columns=['go_group']),right_index=True,left_on='orf_name')

effector_pcc = e_pcc.df.loc[e_pcc.df.eff>np.quantile(e_pcc.df.eff,0.99)]
#effector_sub_pcc = get_subnetwork(e_pcc.graph_gc, effector_pcc.orf_name.values)
#is_effector = dict(zip(effector_sub_pcc.nodes, [True if i in effector_pcc.orf_name.values else False  for i in effector_sub_pcc.nodes]))
#nx.set_node_attributes(effector_sub_pcc, is_effector, 'is_effector')
effectors_connected_comp = sorted([sorted(list(i)) for i in nx.connected_components(nx.induced_subgraph(e_pcc.graph_gc, effector_pcc.orf_name.tolist()))], key=lambda x:x[0])
effector_pcc.loc[:, 'go_group'] = ['mito' if i in effectors_connected_comp[0] else 'golgi' if i in effectors_connected_comp[1] else 'chromatin' for i in effector_pcc.orf_name]
effector_order = effector_pcc.groupby('go_group').eff.median().sort_values().index.tolist()
sensor_order = sensors_pcc.groupby('go_group').sens.median().sort_values().index.tolist()
```

```{python}
from matplotlib.lines import Line2D
pos = e_pcc.graph_gc.nodes('pos')
fig, ax = plt.subplots(figsize=(12,12))
legend_elements = [    ]
e_pcc.plot_network_spring(ax=ax,
                          node_size=1,
                          node_color='black',
 #                        node_size = [100 if i in sensors_pcc.orf_name.values or i in effector_pcc.orf_name.values else 1 for i in e_pcc.nodes],
                         #node_color = ['red' if i in sensors_pcc.orf_name.values else 'blue' if i in effector_pcc.orf_name.values else 'black' for i in e_pcc.nodes],
                         edge_color='black')
#                         node_shape=['^' if i in sensors_pcc.orf_name.values else 'v' if i in effector_pcc.orf_name.values else 'o' for i in e_pcc.nodes])
nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=sensors_pcc.orf_name.values, node_size=200, pos=pos,
                          node_color='black',
                          node_shape='^',edgecolors='black',
                          linewidths=1)
for itr, i in enumerate(sensor_order):
    #print(i, effector_colors[itr])

    orf_names_to_plot = sensors_pcc.loc[sensors_pcc.go_group==i, 'orf_name'].tolist()
    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
                          node_color=sensor_colors[itr],
                          node_shape='^',edgecolors='black',
                          linewidths=1)
    legend_elements.append(
        Line2D([0], [0], marker='^', color='black', label=f'Sensors ({i})',
                              markerfacecolor=sensor_colors[itr], markersize=12, linestyle="None")
    )
nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=effector_pcc.orf_name.values, node_size=100, pos=pos,
                      node_color='black',
                      node_shape='o')
for itr, i in enumerate(effector_order):
    orf_names_to_plot = effector_pcc.loc[effector_pcc.go_group==i,'orf_name'].tolist()
    nx.draw_networkx_nodes(e_pcc.graph_gc, nodelist=orf_names_to_plot, node_size=200, pos=pos,
                          node_color=effector_colors[itr],
                          node_shape='o',edgecolors='black',
                          linewidths=1)
    if i == 'mito':
        lbl = 'Respiratory complex assembly'
    elif i == 'golgi':
        lbl = "Golgi vesicle transport"
    else:
        lbl = 'Chromosome segragation'
    legend_elements.append(
            Line2D([0], [0], marker='o', color='black', label=f'Effectors ({lbl})',
                                  markerfacecolor=effector_colors[itr], markersize=12, linestyle="None")
        )
nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, sensors_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='red', alpha=0.5)
ax.set_facecolor('white')
legend_elements.extend(
    [Line2D([0], [0], marker='o', color='black', label='Genes',
                              markerfacecolor='black', markersize=4, linestyle="None"),
#                    Line2D([0], [0], marker='o', color='black', label='Effectors',
#                               markerfacecolor='black', markersize=10, linestyle="None"),
#                    Line2D([0], [0], marker='^', color='black', label='Sensors',
#                               markerfacecolor='black', markersize=10, linestyle="None"),
                       Line2D([0], [0], marker='o', color='black', label= 'High functional similarity',
                              markerfacecolor='black', markersize=0, linestyle="-"),
                   Line2D([0], [0], marker='o', color='red', label= 'Sensor-Sensor edges',
                              markerfacecolor='#018571', markersize=0, linestyle="-"),
                   Line2D([0], [0], marker='o', color='blue', label= 'Effector-Effector edges',
                              markerfacecolor='#a6611a', markersize=0, linestyle="-")]
)
lgd = ax.legend(handles=legend_elements, fontsize=22,loc='center left', bbox_to_anchor=(1.1, 0.5))

nx.draw_networkx_edges(nx.induced_subgraph(e_pcc.graph_gc, effector_pcc.orf_name.tolist()), ax=ax , pos=pos, edge_color='blue',alpha=0.5)
plt.savefig('tmp_nw.png',bbox_inches='tight')
```

```{r}
effector_pcc = py$effector_pcc
sensors_pcc = py$sensors_pcc%>%mutate(go_group = (as.character(go_group)), go_group=ifelse(go_group=='NULL', NA, go_group))
#library(tidyverse)
eff_deg_comp<-ggplot(effector_pcc%>%mutate(go_group=fct_reorder(go_group, eff)), aes(x= go_group, y=deg,fill=go_group))+
    geom_boxplot()+
    scale_fill_manual(values=effector_colors,
                      labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
    xlab('')+
    ylab('Degree')+
    theme_bw()+
    theme(axis.text.x=element_blank(),legend.title=element_blank(),legend.text = element_text(margin=margin(t=10,b=10)))#, legend.spacing.y = unit(2,'in'))
eff_eff_comp<-ggplot(effector_pcc%>%mutate(go_group=fct_reorder(go_group, eff))%>%
                      mutate(eff_norm =eff / 5183), aes(x= go_group, y=eff_norm,fill=go_group))+
    geom_boxplot()+
    #scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
    xlab('')+
    scale_fill_manual(values=effector_colors)+
    ylab('Effectiveness')+
    theme_bw()+
    theme(axis.text.x=element_blank(),legend.title=element_blank())

sens_deg_comp<-ggplot(sensors_pcc%>%drop_na()%>%mutate(go_group=fct_reorder(go_group, sens)), aes(x= go_group, y=deg,fill=go_group))+
    geom_boxplot()+
#    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
    xlab('')+
    ylab('Degree')+
    scale_fill_manual(values=sensor_colors)+
    theme_bw()+
    theme(axis.text.x=element_blank(),legend.title=element_blank(),
          legend.text = element_text(margin=margin(t=10,b=10)))#, legend.spacing.y = unit(2,'cm'))
sens_sens_comp<-ggplot(sensors_pcc%>%drop_na()%>%mutate(go_group=fct_reorder(go_group, sens))%>%
                      mutate(sens_norm = sens / 5183), aes(x= go_group, y=sens_norm,fill=go_group))+
    geom_boxplot()+
#    scale_x_discrete(labels=c('Chromosome\nSegragetion','Golgi vesicle\nTransport','Respiratory complex\nassembly'))+
    xlab('')+
    ylab('Sensitivity')+
    scale_fill_manual(values=sensor_colors)+
    theme_bw()+
    theme(axis.text.x=element_blank(),legend.title=element_blank())

img <- 'tmp_nw.png' %>%
  magick::image_read() #%>%
  #magick::image_resize("570x380")

nw_img = cowplot::ggdraw()+
    cowplot::draw_image(img, width=1)
go_plots = cowplot::plot_grid(eff_deg_comp+theme(legend.position='none'),
                   eff_eff_comp+theme(legend.position='none'),
                   cowplot::get_legend(eff_deg_comp),
                   sens_deg_comp+theme(legend.position='none'),
                   sens_sens_comp+theme(legend.position='none'),
                   cowplot::get_legend(sens_deg_comp),ncol=3, labels=c('B','C','','D','E',''))

combined = cowplot::plot_grid(nw_img, go_plots,nrow=2,rel_heights=c(0.4,0.6), labels=c('A',''))
ggsave('reports/figures/paper_figures_0916/fig6.png',plot=combined,width=7,height=12)
```
